\documentclass[11pt]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usetheme{Rochester}
\usepackage{graphicx}
\begin{document}
	\title{\textbf{Website Design Ranker}}
	\subtitle{Using Machine Learning}
	%\logo{}
	\institute{\large Department of Computer Science and Engineering \\\textbf{FISAT}}
	\date{15 AUGUST 2019}
	\author{{\scriptsize Adhyaksh Guhan - 7 , Anet Eliza Johny - 23 , Dharwish Raj - 47 , \\ Joel J Padayattil - 60}}
	%\setbeamercovered{transparent}
	%\setbeamertemplate{navigation symbols}{}
	\begin{frame}[plain]
		\maketitle
	\end{frame}
	\begin{frame}{Introduction}
		\begin{itemize}
			\item Our project involves an Machine learning algorithm that uses certain parameters to rank websites in terms of their design.
			
			\item In this presentation, we will be explaining, comparing and contrasting existing works that are similar in purpose to our project.
		
			\item We will be comparing against:
				\item A Website that ranks other design according to submissions by critics
				\item A ranking implementation done by Google that analyses a webpage's contents
				\item An algorithm called CoLiDes models how people navigate a complex website to find information
		\end{itemize}
	\end{frame}
	\begin{frame}{Problem}
		\begin{itemize}
			\item Our main problem is to evaluate website designs using an algorithm that uses machine learning
			\item It must take into account various parts of the website to use as parameters.
	\end{frame}
	\begin{frame}{Why "Website Design Ranker" ?}
		\begin{itemize}
			\item Website Design Ranker will rank set of input webistes as choice of parameter
			\item It will be helpful to find best website among list of websites which have same content
		\end{itemize}
	\end{frame}
	\begin{frame}{Existing Methods}
	\end{frame}
	\begin{frame}{Problem Analysis}
	\end{frame}
	\begin{frame}{What we proposed?}
		\begin{itemize}
			\item We propose a system where an algorithm scrubs through a website, looking for various elements.
			\item Once we discover the nature of these elements, we check whether the parameters we have set (eg: colour, symmetry, etc) have been met.
			\item For each parameter met, a website will obtain a mark.
			\item Once all parameters have been checked, the website receieves an overall score (the sum of all marks) that ranks its design.
	\end{frame}
	\begin{frame}{Conclusion}
		\begin{itemize}
			\item Here we can see the logical differences in the approaches that our algorithm takes versus any existing methods.
	\end{frame}
	\end{document}